Incorporating periodic variability in hidden Markov models for animal movement

### 2016-07-11 paper3.Rnw
Figure num problem fix

<<sim_results, warning=FALSE,echo=FALSE,message=FALSE>>=
ICdat <- readRDS("./sim_results/ICdat.rds")
aa <- readRDS("./sim_results/sim.101.RDS")

>>>>

<<sim_results, warning=FALSE,echo=FALSE,message=FALSE,fig.cap="Simulation test for BIC-optimal approach",fig.width=6,fig.height=4>>=
ICdat <- readRDS("./sim_results/ICdat.rds")
aa <- readRDS("./sim_results/sim.101.RDS")
